Generating Simulated Data

### 2021-03-26 docs/SimData.Rmd
add test fit results

@@

library(FSA)
# VBGF packages all take age and length pairs, reformat from length comp at agecl
# break into 3 chunks of time, "era" 48 years each more like our survey
# subsample after reformatting with uncount because we wouldn't have this many ages

@@

  svvbgf <- svlenage %>%
    dplyr::group_by(species, era) %>%
    group_map(~nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .)))

>>>>

sp_age <- NOBAom_ms$funct.group_ss[, c("Name", "NumCohorts", "NumAgeClassSize")]
sp_age <- sp_age %>%
  mutate(n_annages = NumCohorts * NumAgeClassSize)

@@

library(FSA)
vb1 <- vbFuns()
# VBGF packages all take age and length pairs, reformat from length comp at agecl
# break into 3 chunks of time, "era" 48 years each more like our survey
# subsample after reformatting with uncount because we wouldn't have this many ages

@@

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))

  capelinvbgf <- svlenage %>%
    filter(species == "Capelin") %>%
    group_by(era) %>%
    group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))

  # herringvbgf <- svlenage %>%
  #   filter(species == "Norweigan_ssh", era==1) %>%
  #   group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
  #                 start = vbStarts(length~avgage,data = .))))

#Error in nls(length ~ vb1(avgage, Linf, K, t0), data = ., start = vbStarts(length ~  : 
  #singular gradient with group_map, era 2 and 3
  codvbgf <- svlenage %>%
    filter(species == "North_atl_cod") 
    #group_by(era) %>%
    nls(length~vb1(avgage, Linf, K, t0), data = codvbgf,
                  start = vbStarts(length~avgage,data = codvbgf))
#  era==1   Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: codvbgf
#     Linf        K       t0 
# 104.7120   0.4260   0.2176 
#  residual sum-of-squares: 4109723
# 
# Number of iterations to convergence: 7 
# Achieved convergence tolerance: 2.169e-06

#  all years Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: codvbgf
#     Linf        K       t0 
# 112.4694   0.3912   0.2097 
#  residual sum-of-squares: 7354906
# 
# Number of iterations to convergence: 11 
# Achieved convergence tolerance: 9.964e-06

  hadvbgf <- svlenage %>%
    filter(species == "Haddock") 
    #group_by(era) %>%
    nls(length~vb1(avgage, Linf, K, t0), data = hadvbgf,
                  start = vbStarts(length~avgage,data = hadvbgf))
# all years
#     Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: hadvbgf
#    Linf       K      t0 
# 77.0277  0.3601 -0.3546 
#  residual sum-of-squares: 15637500
# 
# Number of iterations to convergence: 11 
# Achieved convergence tolerance: 4.187e-06

  redvbgf <- svlenage %>%
    filter(species == "Redfish") 
    #group_by(era) %>%
    nls(length~vb1(avgage, Linf, K, t0), data = redvbgf,
                  start = vbStarts(length~avgage,data = redvbgf))
#all years
# Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: redvbgf
#    Linf       K      t0 
# 40.8016  0.1165 -1.6688 
#  residual sum-of-squares: 3197990
# 
# Number of iterations to convergence: 13 
# Achieved convergence tolerance: 8.316e-06

    #dplyr::group_by(species, era) %>%
    #group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
    #              start = vbStarts(length~avgage,data = .))))
